\vspace{-0.25em}\thetitle

### 2009-07-29 paper.tex
...

\Figure{packets-accuracy} shows the \caps{CDF} of p-values of observed packet counts versus our predicted distributions.
While some of the \caps{CDF}s do not remain perfectly straight along the diagonal, overall the tendency is for our predictions to remain accurate.
There is some tendency for the observations to fall at the high and low ends of our predictions, indicating that we are in some cases making predictions that are too narrow.
Still the general adherence to the diagonal shows that oh the whole, the packet predictions remain fairly accurate.
\Figure{packets-uncertainty} shows that while we are not losing much accuracy, we are gaining a great deal of certainty about what the actual packet count will be.
Most of the time, 50\% of the time, we lose all but 20\% of our original uncertainty.
\Figure{packets-entropy} complements this figure, showing what the actual distribution of entropy values for the predictors are.

>>>>

\Figure{packets-accuracy} shows the \caps{CDF} of p-values of observed packet counts versus our predicted distributions.
While some of the \caps{CDF}s do not remain perfectly straight along the diagonal, overall the tendency is for our predictions to remain accurate.
There is some tendency for the observations to fall at the high and low ends of our predictions, indicating that we are in some cases making predictions that are too narrow.
Still the general adherence to the diagonal shows that oh the whole, the packet predictions remain fairly accurate.
\Figure{packets-uncertainty} shows that while we are not losing much accuracy, we are gaining a great deal of certainty about what the actual packet count will be.
Most of the time, 50\% of the time, we discard around 80\% of the original uncertainty.
\Figure{packets-entropy} complements this figure, showing what the actual distribution of entropy values for the six data sets.
